Lens Modeling in \sw

### 2013-09-06 text/tex/spaghetti.tex
shaghetti add
edits

@@

@@

SpaghettiLens is build on top of GLASS \citep{Lubini2012}, that builds and improves upon PixeLens \citep{Saha2004}.
It provides a web based graphical user interface that allows to trace contours with the mouse and identify extremal points by clicking on the image.
\spl then tries to find a mass distribution $\kappa(x,y)$ that reproduces the input parameters.
It provides direct visual feedback by rendering a synthetic image side by side the original image, such that users can directly compare the predictions of their model to the survey image.
It additinally provides plots of the modelled mass distribution and the contour lines of arrival time surface as feedback.

>>>>

\begin{figure}
\includegraphics[height=.3\vsize]{fig/spag6941.png} \\
\includegraphics[height=.3\vsize]{fig/spag7022.png} \\
\includegraphics[height=.3\vsize]{fig/spag6919.png}
\caption{Examples of Spaghetti input.  The models from these appear
  later in Figures \ref{fig:6941}, \ref{fig:7022} and
  \ref{fig:6919}. \label{fig:input-spag}}
\end{figure}

@@

A saddle point is recognizable in a contour map because contours do
not loop around it, they tend to approach and then pull away.  There
is one contour ---the saddle-point contour--- that makes an X on the
saddle point itself.  A saddle point contour may not appear on a plot
(and Figure~\ref{fig:arriv} does not show one.  But we can tell from
the other contours where the saddle-point contour would be.

@@

SpaghettiLens is build on top of GLASS \citep{Lubini2012}, that builds and improves upon PixeLens \citep{Saha2004}.
It provides a web based graphical user interface that allows to trace contours with the mouse and identify extremal points by clicking on the image.
\spl then tries to find a mass distribution $\kappa(x,y)$ that reproduces the input parameters.
Since there is no unique solution, \spl samples the solution space and produces an ensemble of solutions, as described in the paper \citep{Lubini2012}.
It provides direct visual feedback by rendering a synthetic image side by side the original image, such that users can directly compare the predictions of their model to the survey image.
It additinally provides plots of the modelled mass distribution and the contour lines of arrival time surface as feedback.
